### 2012-02-07 paper.tex
Corrected a few typos and added some references

BEMÆRK! Denne tekst er nakket fra et tidligere paper (Carbon,2011). Pre-formed mass-selected platinum particles were soft-landed onto the reactor at room temperature using an inert gas-aggregation source (Mantis Deposition Ltd., Nanogen 50). The particles are formed by gas-phase condensation from a ﬂux of platinum atoms that are sputtered from a 99.99\,\% pure Ru target using a magnetron sputter source. The magnetron is housed in a liquid nitrogen cooled enclosure with a 3 mm diameter aperture at one end. Argon gas is ﬂown into the volume around the magnetron at a rate of 10–120 sccm and is pumped away via the aperture so that a local pressure of 0.1–1 mbar is obtained inside the gas-aggregation zone during operation. The cooled argon gas thermalises the sputtered platinum atoms so that they condense into clusters, which further coalesce to form nanoparticles. The size of the nanoparticles is determined by a number of factors such as magnetron sputter power (typically 20–40 W), rate of gas flow, distance between the target and the exit aperture and the diameter of the exit aperture. Platinum nanoparticles with diameters in the range of 2–16 nm can be produced using the source \cite{Nielsen2010,Nielsen2009}. The nanoparticles are carried by the gas stream through the exit aperture of the aggregation zone, producing a nanoparticle beam that is further reﬁned by a skimmer. The nanoparticle beam is then passed through a quadrupole mass ﬁlter where the ionised fraction (60–80\,\%) of the nanoparticles can be ﬁltered according to their mass-to-charge ratio.

\section{Results}
An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding. Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$. At O$_2$:CO ratio of $\sim13$ and a geometrical Pt-coverage of $\sim0.1\,\%$ lightoff occurs at approximately 180\,$^\circ$C. The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating. After the initial lightoff the sample is cooled to room temperature. When at low temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical lightoff ramp and the subsequent increase in temperature to achieve sustained oscillations is seen. Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a lightoff ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
  \label{fgr:initial_treatment}
\end{figure}
The quantitative same behavior has been reproduced on a large number of samples where oscillations also occur. Generally the oscillations have been seen on samples in a wide coverage and particle size regime, however, a geometrical nanoparticle coverage of 0.1\% gave the most consistent oscillations with other samples being less stable with time.

The oscillations are quantitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim$7\,s.) up to more than an hour. An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}. After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation. After the deactivation the sample quickly regains $\sim$30\,\% conversion. Hereafter the conversion increases linearly with time until approximately 50 \,\% conversion is reached. Shortly after reaching 50 \,\% conversion the sample again ignites and covert all CO to CO$_$2. After a short full conversion period the sample again deactivates and the cycle repeats itself.
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.}
  \label{fgr:full_oscillation}
\end{figure*}
Due to flexibility of the setup the pressure in the reactor volume was also varied to observe any change in behavior of the oscillations. In the pressure range of 0.1\,bar to 1\,bar in the reaction volume no change that could be attributed to the pressure was found. The oscillations does not change frequency nor qualitative behavior significantly from the oscillation shown in Figure \ref{fgr:full_oscillation}. Similarly, only a weak dependence on the CO/O$_$2 pressure was observed. At a CO/O$_$2 ratio of $\sim0.025$ only very small amplitude oscillations were observed. Increasing the CO/O$_$2 to $\sim0.175$ showed a clear oscillations with a clear increase in oscillation amplitude compared to lower CO concentrations as observed by the mass spectrometer data. Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.

@@

\section{Discussion}
The CO/O$_2$ dependence showed oscillations from a ratio of 0.025 to 0.175. Richer CO mixtures than 0.175 could did produce any oscillations in our system. The very oxygen rich mixture needed to provoke oscillations agrees with literature \cite{Singh2010,Hendriksen2005}. The is most likely due to the much higher sticking coefficient of CO on platinum which poisons the nanoparticles during the low reactivity region of the cycle.

@@

Due to long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the system setup which due to its small size has timescales on the order of seconds. It is hence hypothesized that the oscillations is a feature related to the nanoparticles. The particles are maybe oxidized? Subsurface, totally oxidized etc. Digt en smuk historie om dette...

>>>>

BEMAERK! Denne tekst er nakket fra et tidligere paper (Carbon,2011). Pre-formed mass-selected platinum particles were soft-landed onto the reactor at room temperature using an inert gas-aggregation source (Mantis Deposition Ltd., Nanogen 50).
The particles are formed by gas-phase condensation from a flux of platinum atoms that are sputtered from a 99.99\% pure Ru target using a magnetron sputter source. The magnetron is housed in a liquid nitrogen cooled enclosure with a 3\,mm diameter aperture at one end. Argon gas is flown into the volume around the magnetron at a rate of 10-120 sccm and is pumped away via the aperture so that a local pressure of 0.1-1 mbar  is obtained inside the gas-aggregation zone during operation. The cooled argon gas thermalises the sputtered platinum atoms so that they condense into clusters, which further coalesce to form nanoparticles. The size of the nanoparticles is determined by a number of factors such as magnetron sputter power (typically 20–40 W), rate of gas flow, distance between the target and the exit aperture and the diameter of the exit aperture. Platinum nanoparticles with diameters in the range of 2–16 nm can be produced using the source \cite{Nielsen2010,Nielsen2009}. The nanoparticles are carried by the gas stream through the exit aperture of the aggregation zone, producing a nanoparticle beam that is further refined by a skimmer. The nanoparticle beam is then passed through a quadrupole mass filter where the ionised fraction (60-80\%) of the nanoparticles can be filtered according to their mass-to-charge ratio.

\section{Results}
An oscillation measurement is performed by mounting a sample in the setup directly after cluster deposition and anodic bonding. Initially a light-off CO-oxidation measurement is performed where the temperature is increased at 3\,$^\circ$C/min until the sample ignites and achieves full conversion of CO to CO$_2$. At O$_2$:CO ratio of $\sim13$ and a geometrical Pt-coverage of $\sim0.1\%$ lightoff occurs at approximately 180\,$^\circ$C. The temperature ramp is typically continued up to 260\,$^\circ$C whereafter the temperature is decreased at the same rate as the heating. After the initial lightoff the sample is cooled to room temperature. When at low temperature the temperature is again increased at 3\,$^\circ$C/min until sustained oscillations occur. A typical initial treatment is seen in Figure~\ref{fgr:initial_treatment} where both the symmetrical lightoff ramp and the subsequent increase in temperature to achieve sustained oscillations is seen. Often the sample will show oscillations either directly upon lightoff or on the falling temperature ramp.
\begin{figure}[h]
\centering
  \includegraphics[width=9cm]{initial_treatment.png}
  \caption{A typical example of the initial treatment of a new sample. After performing a lightoff ramp where oscillations can been seen the temperature is increased to a constant value where sustained oscillations take place.}
  \label{fgr:initial_treatment}
\end{figure}
The quantitative same behavior has been reproduced on a large number of samples where oscillations also occur. Generally the oscillations have been seen on samples in a wide coverage and particle size regime, however, a geometrical nanoparticle coverage of 0.1\% gave the most consistent oscillations with other samples being less stable with time.

The oscillations are quantitatively similar but the oscillation period varies from a few seconds (the time-constant of the reactor is $\sim7\,$s.) up to more than an hour. An example of a slow oscillation is seen in Figure~\ref{fgr:full_oscillation}. After a short on-cycle where all CO is converted to CO$_2$ the reaction shows a fast deactivation. After the deactivation the sample quickly regains $\sim$30\% conversion. Hereafter the conversion increases linearly with time until approximately 50\% conversion is reached. Shortly after reaching 50\% conversion the sample again ignites and covert all CO to CO$_2$. After a short full conversion period the sample again deactivates and the cycle repeats itself.
\begin{figure*}
  \centering
  \includegraphics[width=17cm]{single_full_oscillation.png}
  \caption{A full oscillation period first showing a steep ignition of the sample followed by an almost immediate de-activation of the sample. For the next 65 minutes the sample slowly recovers activity until full conversion is reached again and the cycle repeats itself.}
  \label{fgr:full_oscillation}
\end{figure*}
Due to flexibility of the setup the pressure in the reactor volume was also varied to observe any change in behavior of the oscillations. In the pressure range of 0.1\,bar to 1\,bar in the reaction volume no change that could be attributed to the pressure was found. The oscillations does not change frequency nor qualitative behavior significantly from the oscillation shown in Figure \ref{fgr:full_oscillation}. Similarly, only a weak dependence on the CO/O$_2$ pressure was observed. At a CO/O$_2$ ratio of $\sim0.025$ only very small amplitude oscillations were observed. Increasing the CO/O$_2$ to $\sim0.175$ showed a clear oscillations with a clear increase in oscillation amplitude compared to lower CO concentrations as observed by the mass spectrometer data. Generally, a tendency towards slower oscillation periods for higher CO/O$_2$ ratio was observed.

@@

\section{Discussion}
The CO/O$_2$ dependence showed oscillations from a ratio of 0.025 to 0.175. Richer CO mixtures than 0.175 did not produce any oscillations in our system. The very oxygen rich mixture needed to provoke oscillations agrees with literature \cite{Singh2010,Hendriksen2005}. The is most likely due to the much higher sticking coefficient of CO on platinum which poisons the nanoparticles during the low reactivity region of the cycle.

@@

Due to long timescales between full conversion and low conversion plateaus the oscillations cannot be attributed to the system setup which due to its small size has timescales on the order of seconds. It is hence hypothesized that the oscillations is a feature related to the nanoparticles. The particles are maybe oxidized? Subsurface, totally oxidized etc. Digt en smuk historie om dette... 
It has already been shown using STM \cite{Hendriksen2002} and FT-IR \cite{Carlsson2006} as well as theoretical studies \cite{Gong2004} that the activity of Pt towards CO oxidation at high pressures is highly dependent on the oxidation state of the surface.
